\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry} % Control margins
\usepackage{hyperref}
\usepackage{titlesec} % Section formatting
\usepackage{enumitem} % List customization
\usepackage[english]{babel}
\usepackage{ragged2e} % For justifying justification
\usepackage{tgheros} % Use TeX Gyre Heros (Helvetica/Arial substitute)
\usepackage{setspace} % For line spacing control
\usepackage[nopatch=footnote]{microtype} % Better typography; skip footnote patch

% --- Font Setup (Using TeX Gyre Heros as primary) ---
\renewcommand{\familydefault}{\sfdefault} % Make sans-serif (now TeX Gyre Heros) the default

% --- Margins (Adjust as needed) ---
\geometry{
    letterpaper,
    top=0.75in,
    bottom=0.75in,
    left=0.75in,
    right=0.75in
}

% --- Hyperlink Setup ---
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Ranjan Shettigar Resume},
    pdfpagemode=FullScreen,
    pdfborder={0 0 0}, % Remove borders around links
}

% --- Spacing Adjustments ---
% Set line spacing slightly more relaxed than pure single spacing (optional, adjust 1.05 as needed)
% \setstretch{1.05}
% Or use singlespacing
% \singlespacing
\onehalfspacing

% Space between paragraphs (like between job description paragraphs)
\setlength{\parskip}{0.6em} % Slightly increased from 0.5em

% Remove default paragraph indentation
\setlength{\parindent}{0pt}

% --- Section Formatting ---
\titleformat{\section}
  {\fontsize{14pt}{16pt}\selectfont\bfseries\sffamily} % 14pt for section headings
  {} % Label
  {0em} % Sep
  {}
\titlespacing*{\section}
  {0pt}
  {2.0ex plus 1ex minus .2ex}
  {1.3ex plus .2ex}

% --- Customize lists ---
\setlist[itemize]{
    leftmargin=*,       % Indent relative to current margin
    nosep,              % No vertical space between items in the same list level
    itemsep=0.3em,      % Slightly increased vertical space between items (adjust as needed)
    label=\textbullet   % Standard bullet point
}

% --- Define commands for Job/Project Titles ---
\newcommand{\entrytitle}[4]{%
    {\fontsize{12pt}{14pt}\selectfont\textbf{#1 | #2 | #3 | #4}}\\[\parskip] % Added space after subheading
}
\newcommand{\projecttitle}[2]{%
    {\fontsize{12pt}{14pt}\selectfont\textbf{#1 | #2}}\\[\parskip] % Added space after subheading
}

% --- Define body text font size macro ---
\newcommand{\bodyfont}{\fontsize{10pt}{12pt}\selectfont}

% --- Disable page numbering ---
\pagestyle{empty}

% --- Contact link macros (phone/email) ---
\newcommand{\phone}[1]{\href{tel:#1}{#1}}
\newcommand{\email}[1]{\href{mailto:#1}{#1}}

% --- Document Start ---
\begin{document}

% --- Header ---
\begin{center}
    {\fontsize{18pt}{22pt}\selectfont\bfseries RANJAN SHETTIGAR} \\[1.2ex]
    {\fontsize{10pt}{12pt}\selectfont
     UDUPI – 576102, INDIA | \phone{+91 9743771347} | \email{ranjanshettigar123@gmail.com} | 
     \href{https://github.com/Ranjan-Shettigar}{GitHub} | 
     \href{https://www.linkedin.com/in/ranjanshettigar}{LinkedIn} | 
     \href{https://ranjan.pages.dev}{Portfolio}}
\end{center}

% --- Introduction ---
{\bodyfont
\justifying
I am an innovative individual seeking employment as a creative associate. Given the opportunity, I believe I can offer your company innovative solutions.
}

% --- Experience Section ---
\section*{EXPERIENCE}

\entrytitle{Intern}{MIT}{Manipal, Karnataka}{2025}
{\bodyfont
\justifying
During my internship, I researched and fine-tuned OpenAI's Whisper models for Kannada using datasets like FLEURS and OpenSLR, training on an NVIDIA A100 GPU. I successfully reduced the Word Error Rate (WER) of Whisper Tiny, Small, and Large V3 Turbo models from 100.7\% to 56.23\%, 100.4\% to \textbf{23.12\%}, and 100.09\% to 26.13\%, respectively. Additionally, I developed \textbf{Dhravani}, a multilingual speech corpus collection tool using Flask, Google OAuth2, and PostgreSQL, enabling audio recording, validation, and automatic syncing to Hugging Face. I deployed the project for \textbf{beta testing} and presented it at the Manipal Entrepreneurship Summit 2025. Furthermore, I created a browser extension called \textbf{Type2Script} for real-time transliteration across Indian languages, enhancing multilingual typing accessibility.
}

\entrytitle{Intern}{Exposys Data Labs}{Bangalore, Karnataka}{2023}
{\bodyfont
\justifying
During my Web Development internship, I created "\textbf{Namaste}," a social media platform like Twitter, and gained practical experience in various aspects of web development.
}

% --- Education Section ---
\section*{EDUCATION}

{\bodyfont
\begin{itemize}
    \item \textbf{Bachelor of Engineering in Information Science \& Engineering | 2025} \\
    NMAM Institute of Technology Nitte, Karkala, Karnataka
    \item \textbf{Diploma - Electronics \& Communication Engineering | 2021} \\
    Indira Shiva Rao Polytechnic, Udupi, Karnataka
    \item \textbf{SSLC | 2016} \\
    U Kamalabai High School, Kadiyali, Udupi, Karnataka
\end{itemize}
}

% --- Projects Section ---
\section*{PROJECTS}

\projecttitle{Deep Learning based Skin Cancer Detection System}{2024}
{\bodyfont
\justifying
Developed a CNN-based diagnostic model using MobileNetV2 and Xception architectures for accurate classification of skin lesions (melanoma, nevus, basal cell carcinoma, etc.) from dermoscopic images. Employed data augmentation, Grad-CAM for interpretability, and achieved \textbf{92.5\%} accuracy.
}

\projecttitle{Advaita – College Fest Management System}{2024}
{\bodyfont
\justifying
Developed a PHP-based College Fest Management System with MySQL integration, manual payment setup, and Gmail SMTP for email notifications. Included secure config management and an admin dashboard for event administration.
}

\vspace{1.5em}

\projecttitle{Task-Minder – Android Task Reminder Application}{2023}
{\bodyfont
\justifying
Developed a simple and intuitive Android application designed to help users schedule and manage tasks, deadlines, and appointments. Key features include recurring reminders, popup notifications, calendar integration, and a user-friendly interface for efficient daily task tracking and organization.
}

\projecttitle{IoT based Biometric Fingerprint Attendance System}{2021}
{\bodyfont
\justifying
Designed and developed a smart attendance system using Arduino, ESP8266, and R307 fingerprint sensor. Integrated biometric authentication with real-time data logging on ThingsBoard IoT platform. Implemented serial communication between Arduino and ESP8266, enabling secure cloud-based storage of attendance records for easy access and analysis.
}

% --- Side Projects Section ---
\section*{SIDE PROJECTS}

{\bodyfont
\begin{itemize}
    \item \textbf{Nextinbox:} An email platform for developers and businesses needing reliable automation.
    \item \textbf{Quanta:} Al-powered chat application built with Google's Gemini API.
    \item \textbf{LinkSync:} A simple web-based tool for organizing the links.
    \item \textbf{Smart Dustbin:} Waste segregation dustbin using audio classification with Seed Studio XIAO.
    \item \textbf{TrackItPay:} A financial management tool for tracking expenses, budgeting and analyzing finances.
\end{itemize}
}

% --- Certifications Section ---
\section*{CERTIFICATIONS}

{\bodyfont
\begin{itemize}
    \item Postman API Fundamentals Student Experts
    \item Career Essentials in Generative AI by Microsoft and LinkedIn.
    \item CS50x: Introduction to Computer Science – Harvard University 2024
\end{itemize}
}

% --- Skills Section ---
\section*{SKILLS}

{\bodyfont
\begin{itemize}
    \item Intermediate in: PCB designing in Multisim Software, Soldering, and MS Office.
    \item Basic in: ARM Controller, Figma, Python, HTML, CSS.
    \item Attention to details, Goal-oriented mindset, Task prioritization.
\end{itemize}
}

% --- Hobbies Section ---
\section*{HOBBIES}

{\bodyfont
\noindent Music Production, Video Editing, Listening Music, Vibe coding, Exploring new technologies.
}

\end{document}
% --- End of Document ---